\documentclass[margin]{res}  

\usepackage{helvet}
\usepackage{hyperref}

\textheight=700pt

\begin{document}

\name{Latyshev Ivan}

\address{Moscow, Russia\\ \textit{\href{https://ru.linkedin.com/in/ivan-latyshev-a8875630a}{Linkedin}}}

\address{ivanlatysev2896@gmail.com\\+7(968)-958-07-86}

\begin{resume}

\section{EDUCATION}
\textbf{Higher school of economics}, Moscow, Russia\\
{\sl Faculty of computer science, Computer science and data analysys}\\
{\hfill GPA: 
7.45\\}
\textbf{Subjects studied: } Maths, Programming on C++ and Python, Algorithms and data structures\\

\section{PROJECTS}
\par
\textbf{ZKB Coffee}: 
The Android application developed by the team "Coffee shop chain with the functionality of adding a point on the map". It contains a working application with a linked Yandex map and fully implemented design and functionality. I was developing the design side of this application.
\\

\section{COMPUTER\\SKILLS}

\textbf{Programming} 
Knowledge in programming languages C++ and Python programming languages, as well as knowledge in algorithms. Also knowledge in fundamentals of industrial programming and teamwork. 

\section{REGALIA}

\textbf{The team Olympiad "Vishaya Proba"}
Diploma of the second degree winner

\textbf{Moscow programming school}
Diploma of successful completion of 4 courses

% Modify the format of each position

\section{EXPERIENCE}

\textbf{No experience}

\section{INTERESTED}

I am interested in team work and working with new projects or developing existing ones. I am more interested in programming on C++ language.

\section{MOTIVATION}

Finally I want to say, that it will be the big honor for me to work in Yandex, because I can learn a lot of new things about working in large companies and learn more things about languages I am using.

\end{resume}

\end{document}
